\section{Skills}
\cvitem{}{JavaScript - TypeScript - Express.js - PostgreSQL - OpenAPI Specification (OAS) - MongoDB - React.js - Next.js - Cascading Style Sheets (CSS) - Koa.js - Prisma ORM - HTML - Mongoose ODM - Material-UI - PGAdmin - Studio3T - Git - VSCode }
%\cvitem{Tools}{Git • VSCode • PGAdmin • Studio3T}
% \cvitem{Interpersonal}{Analytical Reasoning • Communication • Organization Skills • Abstraction • Writing • Research Skills • Critical Thinking}


% \section{Master thesis}
% \cvitem{title}{\emph{Title}}
% \cvitem{supervisors}{Supervisors}
% \cvitem{description}{Short thesis abstract}

\section{Experience}
\cventry{2023}
  {Software Engineer}
  {CodeLink}
  {Remote}
  {}
  {
    CodeLink is a social networking platform for developers to meet and share their skills.
    \begin{itemize}
    	\item Participated in a 4-person Agile team, delivering functionality on time.
    	\item Led the development of a discussion feature, allowing users to create projects, interact via likes and comments; encompassed both frontend and backend responsibilities.
    	\item Enhanced platform reliability by covering 100\% of the features routes with Jest and Supertest, and contributed to potential CI/CD integrations by developing a database seed.
    \end{itemize}
Tech Stack: Typescript, Express, PostgreSQL, Prisma, Next.js, CSS
  }


\cventry{2023}
  {Software Engineer}
  {ticktrack}
  {Remote}
  {}
  {
    Ticktrack is a responsive full-stack web application designed for effective time management using the pomodoro technique.
    \begin{itemize}
    	\item Designed and wireframed UI/UX and data flow.
    	\item Formulated an OpenAPI3.0 specification for the backend routes and illustrated sequence diagrams to fortify a robust engineering approach.
    	\item Engineered the data model, controllers and endpoints using Koa, with data persistence in PostgreSQL.
    	\item Constructed the frontend leveraging the React framework.
    \end{itemize}
  Tech Stack: Javascript, Koa, PostgreSQL, React, CSS
  }
\cventry{2023}
  {Software Engineer}
  {MedusaChat}
  {Remote}
  {}
  {
    Medusa is a web app aimed at generating instant, spontaneous, and anonymous discussions.
    \begin{itemize}
		\item Collaborated in a 2 developer team to transition the codebase from JavaScript to TypeScript, optimizing numerous React components for type safety.
		\item Elevated the platform's accessibility, achieving a 100\% score on Chrome Lighthouse and rectifying all Axe DevTools discrepancies.
		\item Integrated Husky to enhance code quality, implementing automated Git hooks that uphold eslint linting standards and run tests pre-commit.
		\item Orchestrated and implemented integration tests, covering 80\% of the application's pivotal features.
    \end{itemize}
Tech Stack: Typescript, Express, Mongoose, Socket.io, React
  }

\cventry{2020-2023}{Career Break}{Health and well-being}{}{}{}

\cventry{2019}
  {Research Assistant}
  {Berlin Social Science Center (WZB)}
  {Berlin}
  {Part-time}
  {Supported research on digital politics, contributing to subsequent publications and presentations.}

  \cventry{2017 -- 2019}
  {Associate Researcher}
  {Technische Universität Berlin}
  {Berlin}
  {Part-time}
  {Led an interdisciplinary course series designed to merge the fields of philosophy and computer science.}

\section{Education}
\cventry{}
  {Immersive Software Engineering Bootcamp}
  {Codeworks}
  {Remote}
  {}
%  {Engaged in intensive software development/computer science studies and collaborated in diverse teams, quickly adapting to new tech stacks and integrating feedback for continuous improvement.}
  {}  %

\cventry{}
  {Master of Arts, Philosophy of Science and Technology}
  {Technische Universität Berlin}
  {Berlin}
  {\textit{1,3}}
  {}
%  {During my Master's studies, I collaborated closely with engineers in the realm of autonomous driving, researching a critical intersection of philosophy, software design, and machine learning.} 


\cventry{}
  {Bachelor of Arts, Philosophy}
  {Ludwig-Maximilians-Universität}
  {Munich}
  {\textit{1,9}}
  {}
%  {My academic trajectory was characterized by a profound focus on the ethics of technology.}
%  
%\section{Languages}
%\cvdoubleitem{German}{Native proficiency}{English}{Full professional proficiency}
%\cvdoubleitem{French}{Elementary proficiency}{Spanish}{Elementary proficiency}
